# SLC Inventory Questions and Youth Leadership Model Questions

## Intrapersonal
### Self-Understanding-Self-Awareness and Development, Q9, Q10, Q11

I have a good understanding of my personality characteristics, beliefs, and interests.
I am aware of my strengths and weaknesses.
I understand why I act the way I do.

### Personal Contributions-Self-Awareness and Development, Q15, Q16, Q17
When working on a group project, I can easily determine which of my strengths, skills, or ideas might be most
beneficial to the project.
I make sure to contribute my strengths, skills, and ideas to groups I am working with.
I don't hold back from offering up my strengths, skills, and/or ideas if I think the group might be able to benefit from
them.

### Ethics-Personal Behavior, Q21, Q22, Q23
I behave in an ethical manner.
My decisions and actions follow an established code of ethics.
I try to uphold the ethical code within which I am operating.

### Confidence-Personal Behavior, Q36, Q37, Q38
I express my opinions and beliefs with confidence.
I am able to give information to others in a confident manner to help them feel assured during a difficult time.
Even in times when I feel nervous or unsure, I am able to demonstrate confidence in what I am doing or saying.

## Interpersonal

### Productive Relationships-Interpersonal Interaction, Q9, Q10, Q11
I make an effort to develop healthy, trusting, and respectful relationships.
I work to improve important relationships that may not be the best they can be.
I work to maintain productive relationships with those in my life.

### Appropriate Interaction-Interpersonal Interaction, Q12, Q13, Q14
I am able to assess a situation and easily determine socially acceptable behaviors.
I behave according to what is most appropriate for the situation and person I am interacting with.
I respect the boundaries of those I interact with.

### Others’ Contributions-Interpersonal Interaction, Q27, Q28, Q29
When confronted with a particular situation, I can easily determine who might be the best to assist given their
strengths and skills.
I have the skills needed to ensure that everyone in a group is operating from their strengths.
I am able to put people in the roles that fit them best based on their skills and strengths.

### Collaboration-Interpersonal Interaction, Q39, Q40, Q41
I work well in groups.
When on a team, I contribute my fair share of work.
I am able to refrain from taking too much control of a group project or task.

### Verbal Communication-Communication, Q9, Q10, Q11
My verbal communication is concise and to the point.
People easily understand what I am trying to say when I speak.
Others appear engaged and interested when I am communicating with them.

### Writing-Communication, Q19, Q20, Q21
I am able to easily express what I want to say through writing.
When writing, my thoughts come across as understandable to readers.
My writing flows logically and clearly.

### Conflict Negotiation-Communication, Q25, Q26, Q26
When conflict arises, I try to achieve the best possible outcome for all involved rather than try to win.
During conflict, I am able to stay focused on the issue at hand so the conflict does not become a personal attack.
I am good at finding common ground.

## Societal
### Diversity-Civic Responsibility, Q9, Q10, Q11
I make an effort meet people from a wide array of backgrounds and experiences.
I interact regularly with people who are different from me.
I reach out to people from a variety of backgrounds and experiences to be a part of my group or organization.
### Others’ Circumstances-Civic Responsibility, Q12, Q13, Q14
I try to learn about the circumstances facing others to better understand their needs.
I make an effort to understand others' circumstances knowing they might be different from mine.
I consider the circumstances of others before acting or reacting in a certain way.

## Strategic
### Research-Learning and Reasoning, Q9, Q10, Q11
I am able to quickly find what I need from a vast array of available information.
When I come across information, I can easily tell what is credible and what is not.
I try to research multiple sources of information before I come to a conclusion.

### Other Perspectives-Learning and Reasoning, Q12, Q13, Q14
I seek out a variety of perspectives to help me shape my thoughts and opinions.
I try to understand perspectives that are different from mine.
I allow other perspectives to impact how I see the world.

### Reflection and Application-Learning and Reasoning, Q15, Q16, Q17
After an experience, I reflect on what I might do differently the next time.
I try to learn from the past so I don't make the same mistake.
I take what I learned from an experience and integrate it in to my future actions.

### Analysis-Learning and Reasoning, Q21, Q22, Q23
I am good at detecting patterns and trends across a variety of sources of information.
When reviewing information, I look at the details to help me better understand the content.
I can pull out the most important content from a lot of information.

### Evaluation-Learning and Reasoning, Q27, Q28, Q29
When faced with a choice, I am good at weighing out my options.
I prioritize the work I need to do so what is most important or urgent gets done first.
I have good judgment.

### Problem Solving-Learning and Reasoning, Q33, Q34, Q35
I am good at solving complex issues.
I'm good at coming up with a variety of possible solutions to a problem.
I can easily determine the best solution to a problem.

### Decision Making-Learning and Reasoning, Q36, Q37, Q38
I attempt to fully understand a situation before making a decision.
I can make simple decisions quickly and easily.
I use care in making decisions that may have an impact on others.

# Qids

## Intrapersonal
```{r}
"
self_understanding =~ q9 + q10 + q11
personal_contributions  =~ q15 + q16 + q17
ethics =~ q21 + q22 + q23
confidence =~ q36 + q37 + q38
"
```

## Interpersonal

```{r}
"productive_relationships =~ q9 + q10 + q11
appropriate_interaction =~ q12 + q13 + q14
others_contributions =~ q27 + q28 + q29
collaboration =~ q39 + q40 + q41
verbal_communication =~ q9 + q10 + q11
writing_communication =~ q19 + q20 + q21
conflict_negotiation =~ q25 + q26 + q26
"

```

## Societal
```{r}
"
diversity =~ q9 + q10 + q11
others_circumstances =~ q12 + q13 + q14
"
```

## Strategic

```{r}

"
research =~ q9 + q10 + q11
other_perspectives =~ q12 + q13 + q14
reflection_application =~ q15 + q16 + q17
analysis =~ q21 + q22 + q23
evaluation =~ q27 + q28 + q29
problem_solving =~ q33 + q34 + q35
decision_making =~ q36 + q37 + q38
"

```
> 